---
title: "A16 - Machine learning (regression)"
author:
- Bryana Benson
- Conner Bryan
output:
  pdf_document: default
  html_notebook: default
---

Read the Manheim case and then build a linear regression model for predicting the selling price of a car using <http://www.richardtwatson.com/data/manheim.csv>. Follow the principles for residual analysis.

###Libraries
```{r message=FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(dplyr)
```


###Read Data
```{r message=FALSE, warning=FALSE}
data <- read_csv("http://www.richardtwatson.com/data/manheim.csv")

head(data)
```


###Linear Regression
```{r}
reg <- lm(price ~ sale + miles + model, data = data)
summary(reg)
```

$$ \hat{Price} = \beta_0 + \beta_1 (Sale) + \beta_2 (Miles) + \beta_3 (ModelY) + \beta_4 (ModelZ)$$

From the model, the average price of a vehicle, holding all else constant, is $22,890. 
If the car was an online sale, the price increased by $591.70. 
For every additional mile on a car, the price decreases by $0.01.
Relative to ModelX, ModelY cars are worth $5,617 more. 
A ModelZ car is worth $12,240 than the ModelX cars.
Overall, this model explains about 94% of the data and is significant at the 0.01 level. 


###Residual Analysis

####Add residuals to dataset
```{r}
data$residuals <- reg$residuals
```

####Plot residuals
```{r}
ggplot(data,aes(price,reg$residuals)) +
geom_point() +
geom_hline(yintercept = 0, color='red')
```

####Run Shapiro Test for Outliers
```{r}
shapiro.test(reg$residuals)
```
P-value is less than 0.05, so the null hypothesis that the data is normally distributed is rejected. There is evidence of outliers in the data.


####Remove Outliers and re-run Shapiro-Wilk normality test
```{r}
st <- shapiro.test(data$residuals)

while(st$p.value < .05) {
data <- data %>% filter((data$residuals) < max(data$residuals))

mod <- lm(data$price ~ data$miles + data$model + data$sale)

data$residuals <- mod$residuals

st <- shapiro.test(data$residuals)
}

st

```
 P-value is greater than 0.05, so the null hypothesis that the data is normally distributed is not rejected. The data is more normally distributed.
 
 
###Re-run Regression Model
```{r}
reg <- lm(price ~ sale + miles + model, data = data)
summary(reg)
```

This model is run with the normalized data that excludes outliers. As a result, the estimates are no longer impacted by those values.

$$ \hat{Price} = \beta_0 + \beta_1 (Sale) + \beta_2 (Miles) + \beta_3 (ModelY) + \beta_4 (ModelZ)$$
$$ \hat{Price} = 7,129 + 1,347 (Sale) + .073 (Miles) + 5,799 (ModelY) + 12,280 (ModelZ)$$
