---
title: "A18 - Machine Learning (principal components)"
author: 
- Bryana Benson
- Conner Bryan
date: "March 27, 2019"
output:
  pdf_document: default
  html_document: default
---

Using FT Global 500 data, apply forcats::fct_lump() to create five groups of sectors (the top four by number of companies and the rest). Do a principal components analysis.

###Library
```{r message=FALSE, warning=FALSE}
library(readxl)
library(dplyr)
library(corrplot)
library(ggplot2)
```

###Data
```{r message=FALSE, warning=FALSE, include=FALSE}
#read in data
data <- read_excel("FTglobal500.xls", skip = 3)

#omit NA
data <-na.omit(data)
```
Remove omitted data in the dataset to prevent errors.


```{r}
#Select only numeric variables
data.n <- select_if(data, is.numeric)

```
Since PCA works best with numerical data, you'll exclude the categorical variables, and view the correlations.

```{r}
#Correlations of numeric data
corr <- round(cor(data.n),2)
```
The Global Rank in 2014 and 2015 are highly correlated. The Market Value in Millions has a strong negative correlation to Global Rank in 2014 and 2015. Market value and Net income have a moderately - strong positive corrleation.


###PCA prep and Plot

####Data Types
```{r}
#check data types
str(data)

#change Sector data type to factor
data$Sector <- as.factor(data$Sector)

```


```{r}
#Add back Sector column to numeric dataset
data.n$Sector <- data$Sector

#Rename data.n back to data
data <- data.n
```


####Plots
```{r}
plot(data)
```


####Grouping
```{r echo=TRUE, message=FALSE, warning=FALSE}
#Use negative value to collapse the 4 most common groups of Sectors
data$Sector<- forcats::fct_lump(data$Sector, n= -4)

```
fact_lump lumps together least/most common factor levels into "other". In this case, we want to lump together the 4 most common Sectors and leave the rest in Other.

### Principal Component Analysis

The purpose of principal components analysis is to reduce the complexity of a multivariate dataset into a principal components space. It includes the mathematical transformation of number of possibly correlated variables into a smaller number of uncorrelated variables.

```{r}
#run PCA
pca <- prcomp(data[,c(1:9)],center = T, scale=T)
pca
```

You obtain 9 principal components, which shows the correlation between each variable and each prinicpal components.


```{r}
summary(pca)
```

For example, PC1 explains 37% of the total variance, which means that 37% of the information in the dataset can be encapsulated by just that one Principal Component. 

PC2 explains 15% of the variance.

PC1 and PC2 can explain 52% of the variance.


```{r}
biplot(pca)

```

```{r}
#principal component score for each company
pcaScore <- pca$x[,1]

#Plot Sector and Score
ggplot(data=NULL, aes(x=data$Sector,y=pcaScore)) +
 geom_point()
```


