---
title: "Machine Learning - Association Rules"
author:
- Bryana Benson
- Conner Bryan
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

Use Association Rules to do a market basket analysis for Superstore Sales. As a result of your analysis, what advice would you give to Superstore Sales?

###Libraries
```{r remedy01, message=FALSE, warning=FALSE}
library(readxl)
library(readr)
library(arules)
library(arulesViz)
```



#####Data Import
```{r message=FALSE, warning=FALSE}
#import Superstore Sales from directory
sales <- readxl::read_excel("sales.xls")
#Preview first few rows of data
head(sales)
```

#####File Prep

Create a transaction file with the Order ID and Product Name columns. 
```{r}
#Extract Order ID and Product Name columns
t <- sales[,c(2,17)]

#Create a CSV file called "transactions"
readr::write_csv(t, "transactions.csv")

#Convert to transaction file
trans <- arules::read.transactions("transactions.csv", sep = ",", format = "single", cols = c(1,2) )
```

```{r}
summary(trans)
```

```{r}
#Vector of transation sizes
arules::size(head(trans))
```

```{r}
#View first few rows of data in list format
arules::LIST(head(trans))
```


###Assotion Rule Mining

#####Support

+ The proportion of the times an item set occurs in the dataset


+ Vary until you get a response with a small set of rules

#####Confidence

+ Probability that a rule is correct

#####Lift

+ The ratio by which the confidence of a rule exceeds the
expected confidence

+ + 1 indicates items are independent and there is no relationship

+ + Look for lift > 1


####Identify Frequent Item Sets
```{r}
frequentItems <- arules:: eclat(trans, parameter = list(supp = 0.08, maxlen = 5))

arules::inspect(head(trans))

```

```{r}
itemFrequencyPlot(trans, topN = 10, type = "absolute", main = "Item Frequency")
```


#####Apriori Algorithm: Identify Rules
```{r}
rules <- apriori(trans, parameter = list(supp = 0.06, conf = .7, maxlen = 3))
```

```{r}
rules_conf <- sort(rules, by = "confidence", decreasing = TRUE)

inspect(head(rules_conf))
```




