---
title: "Purrr and factors"
output:
  pdf_document: default
  html_notebook: default
author:
  - Bryana Benson
  - Conner Bryan
---

###Libraries
```{r message=FALSE, warning=FALSE}
library("readxl")
library("purrr")
library("tibble")
library("tidyverse")
library("dplyr")
```

###Combining multiple spreadsheets in a workbook

Download the spreadsheet https://www.census.gov/retail/mrts/www/mrtssales92-present.xls. Combine the Agjusted Range of each spreadsheet in the excel workbook to a single dataframe.
```{r}
#Excel spreadsheet in Project Directory
path <- "mrtssales92-present.xls"

#Combine data in each worksheet in excel workbook using the specified range
data <- path %>%
  excel_sheets() %>%
  set_names() %>% 
  map_df(~ read_excel(path = path, sheet = .x, range = "A72:N110"), .id = "sheet")

#Convert to tibble
as_tibble(data)
```

###Normalizing data

Select the columns that include Year, Code, Kind of Business, and Months. Assign names to columns.
```{r}
#Select columns
data <- data[,c(3,1,4:15)]

#Add names to columns
names(data)[1:14] <- c("Business","Year", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")

#Preview data
head(data)
```


Gather data and make 'Month' a factor.
```{r}
#Gather data: Each month column becomes a single column called 'Month' and the values associated are recorded in the 'Sale' column.
data.g<- gather(data,'Month','Sale',3:14)
```

Make Month a factor and specify levels.
```{r}
#Check data types
str(data.g)

#Specify levels and Make Month a factor
levels <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")

data.g$Month <- factor(data.g$Month, levels)

#Check data types again
str(data.g)

#Preview 20 rows of data
head(data.g, n = 20)
```


###Calculations

Compute average "Retail and food services sales, total" for each month.
```{r}
data.g %>% 
  filter(str_detect(Business, "Retail and food services")) %>% 
  group_by(Month) %>% 
  summarize("Average Sales" = mean(Sale))
```

Get rid of null values in the dataset that is causing
```{r}
#omit NAs
data.g <- na.omit(data.g)
```

```{r}
#Rerun the previous code
data.g %>% 
  filter(str_detect(Business, "Retail and food services")) %>% 
  group_by(Month) %>% 
  summarize("Average Sales" = mean(Sale))
```




